\textbf{ANALYSIS OF \\ MACHINE LEARNING \\ APPLIED TO BOARD GAMES}

### 2022-10-07 doc/paper.tex
added todo list

@@

\section{Introduction}

>>>>

\section*{\huge Todo}
\addcontentsline{toc}{section}{Todo}

\noindent
Regularization: Tikhonov \\
Network Architecture: Depth-Breadth \\
Ensamble methods: Dropout \\
Vanishing/Exploding Gradient: ReLU, Sigmoid \\
Convergence: \\ 
Local Optima: Pretraining \\
Prove nonlinearity's importance: identity function \\
Parameter Reduction: Deeper networks \\
ResNet: Skip Connections \\
\bigskip
Long Short-Term Memory: "forgetting" \\
ConvNet: "forgetting", feature maps, pooling, ReLU \\
RecurrentNet: sequence of moves \\
Stochastic Gradient Descent: Mini-Batch, Point \\
Learning Rate Decay: Exponential and Inverse Decay \\
Momentum-Based Learning: Nesterov Momentum, AdaGrad, RMSProp, \\ AdaDelta, Adam \\
Acceleration and Data Compression: GPU, SIMD ... \\
Overfitting: Penalty Regularization, Ensamble Methods, \\ Early Stopping, Pretraining, Continuation Methods 
Imitation Learning: Supervised

@@

\newpage
\section{Introduction}
